External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-29 CVPR2017_Review_Unified.tex
a

\subsection{Comparison with External and Internal Priors}
In this section, we compare our proposed method on real image denoising with external prior based method (denoted as "External") and internal prior based method (denoted as "Internal"). All the three methods perform real image denoising under the weighted sparse coding framework in Equ. (\ref{equ5}). The "External" method employs the external dictionaries (i.e., $r=0$ in Equ. (\ref{equ5})) to recover the latent clean images, while the "Internal" method employ the GMM to directly cluster the internal noisy PGs into multiple subspaces, and perform denoising with internal dictionary learning (i.e., $r=128$ in Equ. (\ref{equ5})) for each subspace. All parameters of the three methods are tuned to achieve corresponding best performance.

We compare the three methods on the 60 cropped images from \cite{crosschannel2016}. The average PSNR results of these methods are listed in Table \ref{tab1}. It can be seen that our proposed method achieves higher PSNR results then the "External" and "Internal" methods. We also compare the visual qualities of denoised images listed in Figure \ref{fig2} and Figure \ref{fig3}. We can see that the "External" method is good at recovering structures (Figure \ref{fig2}) while the "Internal" method is good at recovering complex textures (Figure \ref{fig3}). And if we make use of both the external and internal priors, our proposed method can recover well both the structures and textures.

In summary, the proposed algorithm achieves better performance on denoising real images than the external and internal prior based methods.

>>>>

\subsection{Comparison with External and Internal Priors}
In this section, we compare our proposed method on real image denoising with external prior based method (denoted as "External") and internal prior based method (denoted as "Internal"). All the three methods perform real image denoising under the weighted sparse coding framework in Equ. (\ref{equ5}). The "External" method employs the external dictionaries (i.e., $r=0$ in Equ. (\ref{equ5})) to recover the latent clean images, while the "Internal" method employ the GMM (with also $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and perform denoising with internal dictionary learning (i.e., $r=3p^{2}$ in Equ. (\ref{equ5})) for each subspace. All parameters of the three methods are tuned to achieve corresponding best performance.

We compare the above mentioned three methods on the 60 cropped images from \cite{crosschannel2016}. The average PSNR results of these methods are listed in Table \ref{tab1}. It can be seen that our proposed method achieves higher PSNR results then the methods of "External" and "Internal". We also compare the visual quality of the images denoised by these methods. From the results listed in Figure \ref{fig2} and Figure \ref{fig3}, we can see that the "External" method is good at recovering structures (Figure \ref{fig2}) while the "Internal" method is good at recovering internal complex textures (Figure \ref{fig3}). And by making use of both the external and internal priors, our proposed method can recover well both the structures and textures.

In summary, the proposed algorithm achieves better performance on denoising real noisy images than the external prior based method and internal prior based method.
